Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-11 paper/ms.tex
Add summary of actions + Gaia dr2

>>>>

In a slowly-evolving, axisymmetric potential, the actions of each star are
time-invariant \citep{2008gady.book.....B}. In the Milky Way, stellar actions
are expected to evolve on short time scales due to scattering with gas clouds
and on long time scales due to resonances with spiral arms, bar(s), and other
large scale perturbations \citep{2014RvMP...86....1S}. For this reason, we and
other authors have used actions to study stellar scattering in the Milky Way
disk using the improved astrometry of {\em Gaia} DR2 and various age
catalogues \citep{2018ApJ...867...31B,2018arXiv180803278T}. Actions have also
been used to study different models of spiral structure in the Milky Way
\citep{2019MNRAS.tmp..155S}. A summary of the disk in action space is given by
\citet{2018arXiv180503653T}.
